---
title: "R Notebook"
output: html_notebook
author: JIEUN PARK - 100509696
---

# Social media related CNN news articles: "How does the U.S. think of social media?"

I collected the text data from CNN news articles to investigate the trends and public opinion related to social media in the United States.

1.  First article: Florida governor signs law restricting social media access for children

CNN News article titled "Florida governor signs law restricting social media access for children." I chose this text to investigate the people's opinion on restricting social media access for children in the U.S. Some people would agree that law for restricting children social media access is necessary to protect them from harmful contents but, on the other hand, the other side of people argue that this law would infringe on teen's First Amendment rights to access the information.

2.  Second article: Judge rules YouTube, Facebook and Reddit must face lawsuits claiming they helped radicalize a mass shooter

A New York state judge on Monday denied a motion to dismiss a lawsuit against several social media companies alleging the platforms contributed to the radicalization of a gunman who killed 10 people at a grocery store in Buffalo, New York in 2022, court documents show.

3.  Third article: Supreme Court to debate whether White House crosses First Amendment line on social media disinformation

Biden administration officials have for years persuaded social media platforms such as Facebook and X to take down posts that include misinformation about vaccines, the Covid-19 pandemic and the 2020 election, among other things.

But the Supreme Court must now decide whether those efforts go too far -- when the government, in other words, veers into censorship on social media that violates the First Amendment.

4.  Fourth article: The 26-year-old YouTuber conquering French journalism

HugoDecrypte's Instagram account has more followers than Le Monde, the French daily widely considered the country's newspaper of record, as well as BFMTV and France24, arguably the two most popular 24-hour news networks in France. And its daily news update is the most downloaded podcast in the country, according to media monitor ACPM.

Whatever you call him, there's no denying that Travers has created something that resonates with young audiences shunning traditional media in France, where mistrust of the news industry runs deeper than in much of the rest of Europe.

5.  Fifth article: More than a third of teens say they spend too much time on their phones, new study finds

Around 40% of teenagers say they have cut back on their time on social media, according to a report published Monday by the Pew Research Center. Nearly the same proportion of teens acknowledge that they spend "too much" time on their smartphones (38%) and social media (27%).

***\<Following process is for the web crawling but since I have saved data into .csv format, you can use it directly.\>***

## Data (text) crawling and Tokenization

```{r}
rm(list=ls())
install.packages("xml2")
install.packages("stringr")
install.packages("rvest")
install.packages("tidytext")
install.packages("tibble")
install.packages("dplyr")
install.packages("tidyr")
library(xml2)
library(stringr)
library(rvest)
library(tidytext)
library(tibble)
library(dplyr)
library(tidyr)

CNN_url_1 <- "https://edition.cnn.com/2024/03/25/tech/florida-social-media-law-age/index.html"

CNN_url_2 <- "https://edition.cnn.com/2024/03/19/tech/buffalo-mass-shooting-lawsuit-social-media/index.html"

CNN_url_3 <- "https://edition.cnn.com/2024/03/17/politics/supreme-court-social-media-disinformation-first-amendment-covid-election-2024/index.html"
  
CNN_url_4 <- "https://edition.cnn.com/2024/03/16/media/france-hugodecrypte-youtube-profile-travers-intl-cmd/index.html"
  
CNN_url_5 <- "https://edition.cnn.com/2024/03/11/tech/teens-feelings-social-media-pew-study/index.html"

CNN_urls <- c(CNN_url_1, CNN_url_2, CNN_url_3, CNN_url_4, CNN_url_5)
```

## Tokenize the text at once

```{r}
# Make the custom_stop_words to filter meaningless words
custom_stop_words <- bind_rows(tibble(word=c("cnn", "social", 
                                             "media", "travers", "news", "platforms"), 
                              lexicon=c("custom", "custom", "custom", 
                                        "custom", "custom", "custom")),
                               stop_words)

merged_tibble <- tibble(word = character(), n = numeric())

# Loop through each URL
for (i in seq_along(CNN_urls)) {
  # Read HTML content from the current URL
  text <- read_html(CNN_urls[i]) %>%
    html_elements(xpath = "//div[@class='article__content']") %>%
    html_text() %>%
    gsub("\n", "", .) %>%
    gsub("—", "", .) %>%
    str_replace_all("[()]", "")
  
  # Create a tibble from the processed text
  tibble_text <- tibble(text)
  
  # Apply unnest_tokens to the tibble
  tidy_text <- tibble_text
    
  # Merge the current tibble with the merged_tibble based on the "word" column
  merged_tibble <- rbind(merged_tibble, tidy_text)
}

print(merged_tibble)

install.packages("readr")
library(readr)

# To save the time I saved the tibble as the dataset 
write_csv(merged_tibble, "merged_tibble.csv")

```

### CSV data: merged_tibble.csv

```{r}
# Therefore now it can be used by using read.csv function
merged_tibble <- read.csv("merged_tibble.csv")

# Sum the counts for each word across all tibbles
tidy_merged_tibble <- merged_tibble |> unnest_tokens(word, input = text) %>%
    anti_join(custom_stop_words) |>  count(word, sort = TRUE)

# Print the merged tibble
print(tidy_merged_tibble)
```

I collected the text data from the CNN news article related to **social media**. I have used the web crawling method to get the text data by the "rvest" library and used "stringr", "tidytext", and "tibble" to tokenize the text into words. After making the text into words, I filtered the stop_words and used the count function to see the overall number of word counts using the "dplyr" library. Then I visualize the 5 most frequent words in the article.

### Graph 1. Overview of the words count from the CNN new article related to social media

```{r}
#install.packages("ggplot2")
library(ggplot2)

tidy_merged_tibble |> filter(n > 5) |> mutate(word = reorder(word, n))|> 
                 ggplot(aes(n, word)) + geom_col(show.legend = FALSE, fill = "skyblue") +
                 theme_minimal() + labs(y = NULL, x = NULL)
```

The most frequent words in the 5 CNN news articles related to social media are "teens", "court", "government", "companies", and "youtube". From this graph, we can assume that the trends related to social media in the United States are that the government focuses on teenagers' social media usage such as YouTube, and some social media companies have been sued and have a trial in the court.

### Sentiment analysis

```{r}
#install.packages("tidytext")
#install.packages("textdata")
library(tidytext)
library(textdata)

get_sentiments("afinn")
get_sentiments("bing")
get_sentiments("nrc")

# See the word count with sentiment type
word_sentiment <- tidy_merged_tibble |> inner_join(get_sentiments("bing"))
print(word_sentiment)

# Check the total number of words for each sentiment: negative and positive.
word_sentiment |> group_by(sentiment) |> summarise(total = sum(n)) |> ungroup()
```

### Graph 2. each words

```{r}
# Words count by each sentiment
word_sentiment |> filter(n > 1) |>  mutate(word = reorder(word, n)) |>  
  ggplot(aes(n, word, fill = sentiment)) + 
  geom_col(show.legend = FALSE) +
  theme_minimal() + labs(x=NULL, y=NULL) + 
  facet_wrap(~sentiment, ncol=2, scales="free")
```

The most frequent words related to the social media CNN news article are "conservative", "harm", "violate", "threaten", "suppress", and "prohibit" for the negative sentiment and "supreme", "free", "trust", "popular", and "success" for the positive sentiment. Therefore, we can assume that people from the United States think of social media with those words and sentiments.

### Graph 3. each sentiment

```{r}
# Total word counts by each sentiment
word_sentiment |> group_by(sentiment) |> summarise(total = sum(n)) |> ungroup() |> 
  ggplot(aes(total, sentiment, fill = sentiment)) + 
  geom_col(show.legend = FALSE) +
  theme_minimal() + labs(x=NULL, y=NULL) 
```

From graph 3, we can see there are more negative words (101) than positive words (62) in the CNN news articles related to social media. Therefore, we can assume that when people portray social media then they use more negative words than the positive words in the United States.

### N-grams analysis

```{r}
# Tokenizing the text into bigrams
news_bigrams <- merged_tibble |> unnest_tokens(bigram, text, token = "ngrams", n = 2) |> 
  filter(!is.na(bigram)) |> 
  separate(bigram, c("word1", "word2"), sep = " ") |> 
  filter(!word1 %in% custom_stop_words$word) |> 
  filter(!word1 %in% custom_stop_words$word) 

# countr the bigrams
bigram_counts <- news_bigrams %>% 
  #how many times in the bigrams_filtered they appear together
  count(word1, word2, sort = TRUE)

bigram_counts

# Unite the bigrams
bigrams_united <- news_bigrams %>%
  unite(bigram, word1, word2, sep = " ")

bigrams_united
```

Secondly, I did the n-gram analysis using **"bigrams"**. There are in total 8 bigrams with the words "supreme" and "court" combination. From this, we can assume that nowadays many social media-related trials have been done in the United States. Next, "time"+"on", "content"+"that", and "biden"+"administration" is the most frequently used word combinations as bigrams in the CNN news articles for social media topic in the United States.

### Graph 4. Bigrams wordcloud

```{r}
install.packages("wordcloud2")
library(wordcloud2)

set.seed(700)

bigrams_united %>%
pull(bigram) |> table() |> sample(size = 100) |> 
  wordcloud2(color = "random-dark",
            fontWeight = 550,
            size = 0.4,
            widgetsize = c(900, 500))

```

From graph 4, we can see bigram kinds from the CNN news articles related to social media. Some of them are "private entities", "feel anxious", "instagram or", teens and", and "pass laws."

## Tokenize text by articles

```{r}
tibble_list <- list()

for (i in seq_along(CNN_urls)) {
  # Read HTML content from the current URL
  news <- read_html(CNN_urls[i]) %>%
    html_elements(xpath = "//div[@class='article__content']") %>%
    html_text() %>%
    gsub("\n", "", .) %>%
    gsub("—", "", .) %>%
    str_replace_all("[()]", "")
  
  tibble_text <- tibble(news)
  
  # Store the text in the list
  tibble_list[[i]] <- tibble_text
}

merged_tidy_news <- bind_rows(tibble_list, .id = "source") %>%
  mutate(source = paste("Source", row_number())) 

# Save the merged_tidy_news as csv data
write_csv(merged_tidy_news, "merged_tidy_news.csv")
```

### CSV data: merged_tidy_news.csv

```{r}
# Read csv to get the data
merged_tidy_news <- read.csv("merged_tidy_news.csv")

merged_tidy_news_words <- merged_tidy_news |> unnest_tokens(word, news) |>
                          anti_join(custom_stop_words) 
```

### Visualization

```{r}
install.packages("ggplot2")
library(ggplot2)

merged_tidy_news_words |> count(source, word, sort=TRUE) |>  group_by(source) |> 
             filter(n > 3) |> ungroup() |> 
             mutate(word = reorder(word, n)) |> 
             ggplot(aes(n, word, fill = source)) + 
             geom_col(show.legend = FALSE) +
             facet_wrap(~factor(source, levels = c("Source 1", "Source 2", 
                                                 "Source 3", "Source 4", "Source 5")),
                        ncol=5, scales="free") + theme_minimal()
```

Five different articles have different words distributions.

In the first article, there are words such as "legislation", "law", "florida", and "accounts." We can assume that this article is related to Florida law legislation related to social media and its users who have their accounts.

In the second article, there are words such as "court", "companies", "reddit", and "decision." We can assume that this article is about a trial related to social media companies such as reddit and some kind of decision has been made from the court.

In the third article, there are words such as "government", "court", "amendment", "biden", "administration", "private", "disinformation", and "decision." We can assume that the Biden administration announced or made some decisions related to the social media disinformation problem.

In the fourth article, there are words such as "french", "hugodecrypte", "youtube", journalism", and "channel." We can assume that in French YouTube, there is a hugodecrpyte channel and it should be related to journalism.

Finally, in the fifth article, there are words such as "teens", "parents", "smartphones", and "time." Therefore, we can assume that teens have a problem related to smartphone usage time using social media and theses problems somehow require their parents' help.

### Sentiment analysis

```{r}
library(tidytext)
library(textdata)

news_sentiment <- bind_rows(
  #Bing
  merged_tidy_news_words %>% 
    #we get sentiments from bing
    inner_join(get_sentiments("bing")) %>%
    #we create the column for bing
    mutate(method = "Bing et al."),
  #NRC
  merged_tidy_news_words %>% 
    #we get sentiment from nrc 
    inner_join(get_sentiments("nrc") %>% 
                 #we filter just sentiment, not emotions
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    #we create the column for nrc
    mutate(method = "NRC")) %>%
  #we divide in chunks of 80 lines
  count(method, index = rep(1:(n() %/% 80), 
                                  each = 80, length.out = n()), sentiment, word) %>%
  #we write positive and negative in different columns
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  #we extract net sentiment by substraction
  mutate(sentiment = positive - negative)
```

### Graph 5. Sentiment analysis

```{r}
# Comparison between bing and nrc
news_sentiment |> slice_max(abs(sentiment) > 1) |> 
                  mutate(word = reorder(sentiment, word)) |> 
                  ggplot(aes(sentiment, word, fill = method)) + 
                  geom_col(show.legend = FALSE) +
                  facet_wrap(~method, ncol=2, scales="free") +
                  theme_minimal() + labs(x="net sentiment", y=NULL)

afinn <- merged_tidy_news_words %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(word, index = rep(1:(n() %/% 80), each = 80, length.out = n())) %>% 
  summarise(sentiment = sum(value)) %>% 
  ungroup() %>% 
  mutate(method = "AFINN")

# comparison among bing, nrc, and afinn
bing_afinn_nrc <- bind_rows(afinn, news_sentiment) %>%
  select(word, index, sentiment, method) 

bing_afinn_nrc |> 
              filter(abs(sentiment) > 2) |> 
               mutate(word = reorder(word, sentiment)) |> 
               ggplot(aes(sentiment, word, fill = method)) + 
               geom_col(show.legend = FALSE) +
               facet_wrap(~method, ncol=3, scales="free") +
               theme_minimal() + labs(y=NULL, x="net sentiment")

bing_afinn_nrc |> group_by(method) |> 
                  slice_max(sentiment, n=1) |> ungroup()

bing_afinn_nrc |> group_by(method) |> 
                  slice_min(sentiment, n=1) |> ungroup()
```

From the AFINN, "popular" has the highest positive net sentiment (9), and "harm" has the highest negative net sentiment (-8). From Bing et al., "supreme" has the highest positive net sentiment (7), and both of "conservative" and "harm" have the highest negative net sentiment (-3). From the NRC, "content" has the highest positive net sentiment (6), and "government" has the highest negative net sentiment (-11). Overall, the AFINN lexicon is biased to negative words, and both Bing et al. and NRC lexicons are biased to positive words. This word's sentiment distribution provides insights from words which have either positive or negative sentiments that the U.S. people would use to describe the social media-related things in the news article.

### TF-IDF

```{r}
library(dplyr)
library(tidytext)

total_words <- merged_tidy_news_words |> count(source, word, sort=TRUE) |>
  group_by(source) |> summarize(total = sum(n)) |> ungroup()

# word count
news_word_count <- merged_tidy_news_words |> count(source, word, sort=TRUE) 

# calcuate the term frequency
news_word_count_total <- left_join(news_word_count, total_words)
news_word_count_total <- news_word_count_total |> 
  mutate(term_frequency = n/total)

# TF-IDF
news_tf_idf <- news_word_count %>%
  bind_tf_idf(word, source, n)
```

The more documents containing the word, the less distinctive it is of any of them, so the TF-IDF metric will be higher for words that occur fewer times.

### Graph 6. Term frequency

```{r}
library(ggplot2)
news_word_count_total |> group_by(source) |>  slice_max(term_frequency, n=5) |> 
  ungroup() |> mutate(word = reorder(word, term_frequency)) |> 
  ggplot(aes(term_frequency, word, fill = source)) +
  geom_col(show.legend=FALSE) +
  facet_wrap(~source, ncol=2, scales="free") +
  theme_minimal() + labs(y=NULL, x="Term Frequency")
```

The term frequency graph shows the overall term frequency distribution by each article source. The top words that have the highest term frequency in article 1 are "legislation", "law", and "florida" For article 2, words are "content", "court", "reddit", "decision", and "companies." For article 3, the words are "government", "court", "companies", "amendment", and "supreme." For article 4, the words are "french", "hugodecrypte", "yotube", "audiences", and "people." Finally, for article 5, words are "teens", "report", "parents", "smartphones", "teen", "phones", and "pew." By these keywords from each article, we can assume the article' stories and approximate atmosphere related to social media in the United States without reading the whole article.

### Graph 7. TF-IDF

```{r}
#install.packages("forcats")
library(forcats)

news_tf_idf %>%
  group_by(source) %>%
  #choose maximum number of words
  slice_max(tf_idf, n = 8) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(word, tf_idf), fill = source)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~source, ncol = 3, scales = "free") +
  labs(x = "tf-idf", y = NULL)

```

When the value of TF-IDF is high then it means the words are rare among the documents. The words having the highest TF-IDF from the first article are "law", "florida", and "accounts." We can say since florida is a state name it can have the highest TF-IDF value. In the second article, words are "reddit", "statement", "lawsuit", and "court." In the third article, the words are "government", "court", and "speech." In the fourth article, the words are "french", "hugodecrypte", and "audiences." Finally, from the fifth article, the words are "teens", "smartphones", and "report." As we realize from the first article words, when there are pronouns then they tend to have the highest TF-IDF value since it will have less possibility to appear on the same CNN news articles. For example, from article 4, "hugodecrpyte" is a specific YouTube channel name so it is the word that has the highest TF-IDF values. Moreover, from the TF-IDF analysis, we can approximately capture the story of the News article because it shows us the keywords that are the most important from the articles. Therefore, with this process, we can get not only the flow of the CNN news articles' stories but also current situations in the United States related to social media without reading the whole article.

## Conclusion

In conclusion, I have used three different techniques which are "sentiment analysis", "n-grams analysis", and "TF-IDF analysis" by using data from CNN news articles related to social media topics. Data sets are processed in two different ways: first, words from news articles have been processed regardless of resource articles, and second, words are separately labeled by each resource article. Overall analysis and its interpretation with graphs provide profound insights into understanding current perspectives and trends of social media in the United States. Moreover, by using the text mining method, we can assume and approximately understand the article contexts without reading the whole CNN news articles which enables us to save a lot of time for reading articles.

Therefore, the insight that I was able to capture from five different CNN news articles related to social media is that, nowadays, the U.S. government has restricted social media companies due to the disinformation dispersion possibility, increased teenagers' smartphone usage time, and the possibility that teenagers easy access to the harmful contents through social media platforms. This insight was able to be gained by articles 1, 2, 3, and 5. From article 4, I was able to know as social media platforms are getting popular, content producers such as "YouTubers" from the YouTube platform have more social influence even sometimes over public broadcasting services.
